Randomized trace estimation for parameter-dependent matrices applied to spectral density approximation

### 2024-09-07 paper/re-pro-badge.tex
automatically reproduce paper

The code for our numerical experiments can be found on \url{https://github.com/FMatti/Rand-TRACE}. The figures and tables were generated from the commit \href{https://github.com/FMatti/Rand-TRACE/tree/d86c14f}{d86c14f} on 2024-08-21 at 12:47:34 UTC.

>>>>

The code for our numerical experiments can be found on \url{https://github.com/FMatti/Rand-TRACE}. The figures and tables were generated from the commit \href{https://github.com/FMatti/Rand-TRACE/tree/9c36faf}{9c36faf} on 2024-09-07 at 07:01:11 UTC.
